Pricing Kernels and Risk Premia implied in Bitcoin Options

### 2024-01-07 written/paper.tex
writing

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Pricing Kernels and Risk Premia implied in Bitcoin Options},
  pdfauthor={Julian Winkel; Wolfgang K. Härdle},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.5cm]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{caption}
\usepackage{eucal}
\floatplacement{figure}{H}

\title{Pricing Kernels and Risk Premia implied in Bitcoin Options}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{21 November 2022}

@@

\singlespacing 
Bitcoin Pricing Kernels (PK) are estimated using a novel data set from Deribit, the leading Bitcoin options exchange. The PKs, as the ratio between risk-neutral and physical density, dynamically reflect the change of investor preferences. Thus the PKs improve the understanding of investor expectations and risk premium in a new asset class. Bootstrap-based confidence bands are estimated in order to validate the results. Investors are heterogeneous in their risk profiles and preferences with respect to volatility and investment horizon. The empirical PKs turn out to be U-shaped for short-dated instruments and W-shaped for long-dated instruments. We find that investors are willing to pay a substantial risk premium to insure themselves against short-term price movements. The risk premium is smaller for longer-dated instruments and their traders are risk averse. The shape of the empirical PKs reveals the existence of a time-varying risk-premium. The similarity between the shape of empirical PKs for Bitcoin and other markets that represent aggregate wealth shows that Bitcoin is becoming an established asset class.

@@

The valuation of digital currencies has been a question that predated
its first representative, Bitcoin. Upon the creation of Bit Gold, Szabo
(2008) envisioned its value to arise from an interplay between the
benefits of the two entities which foremost represent value: cash and
metal. The argument put forward was that metal bears an inherent value
that is largely independent of trusted third parties. However, the
unwieldiness of metal incurs a relatively high transaction cost when
used as a means of exchange. (Unbacked) Cash, on the other hand, draws
its value largely from the trust in a third party's acceptance. The
combination of the two elements, coming in the form of a scarce digital
resource that is governed in a trustless system, has been passed on to
Bitcoin (BTC) and other Cryptocurrencies (CC).

Since the inception of BTC as proposed by Nakamoto (2009), various
arguments have been made on its valuation. Apart from the benefit of a
trustless system, the arguments typically include the production cost of
a block (Hayes 2019), the benefit of borderless transactions (Deng 2020;
Stellar Development Foundation 2022), the value of an inflation hedge
(Choi and Shin 2022), network effects (Chen and Vinogradov 2021; Gandal
and Halaburda 2016) or expectations about future price developments
(Blau 2017; Smaniotto and Neto 2022).

In addition to the former valuation approaches, we offer new insights by
means of the BTC derivatives market which has emerged over the course of
the last years. Since derivatives markets are particularly rich in
information, their evolution provides a unique opportunity to assess the
BTC market valuation through the application of proven econometric
techniques. Key information about preferences and forward looking
decisions are state price densities (SPD), that can be estimated from
option prices. SPDs yield risk-neutral probabilities, under which
investors price derivatives. They provide the key to pricing exotic or
illiquid options in an arbitrage-free manner (Aït-Sahalia and Lo 1998)
and offer insight into changing expectations about future developments.
In conjunction with the physical density (PD) of Bitcoin returns, the
resulting pricing kernels (PK) can be calculated. The shape and
evolution of PKs over time discloses investor expectations under
different market circumstances and gives insight into time varying
preferences. We present the first paper that is based on real Bitcoin
option data, inferring and disclosing investor preferences following
hypothesizing papers on bootstrap-based confidence bands for empirical
PKs (Härdle et al. 2014) and cryptocurrency option pricing under an SVCJ
model (Hou et al. 2020).

BTC derivatives markets can already be regarded as efficient information
processing mechanisms (Alexander et al. 2022). Among those markets,
\href{https://www.deribit.com/}{Deribit} is the leading crypto option
exchange as measured by open interest and trading volume. As of
2022-07-25, Deribit manages more than 90\% of the BTC option volume
which translates over a 30 day window into an average 24-hour trading
volume of over 331.8 million USD (Skew.com 2022). The competitors
LedgerX, OKEx, CME, bit.com and Binance are contributing respective
averages of 1.9, 15.7, 13.2, 1.5, 0.582 million USD.

A particularly interesting property of the BTC options market is its
decentralized nature. Trading on Deribit is largely dominated by
retailers. Despite an ongoing decline of retail market share in favor of
institutions (Coinbase 2022), who are cautious to invest in highly
volatile and unregulated assets, the options market on Deribit remains
driven by retailers: As of 2022-07-25, 86.65\% of the volume is
attributed to retail, whereas 9.16\% and 1.19\% are attributed to
investors and whales (Deribit 2022a). Deribit classifies market
participants according to their share of the circulating BTC supply.
According to Deribit's classification, a ``whale'' is an entity that
owns more than 1\% of the supply on Deribit, an ``investor'' owns
between 0.1\% and 1\% and a ``retailer'' owns less than 0.1\%.
Considering the retail share in trading volume in conjunction with
Deribit's dominating market share over the competition, we figure that
the Bitcoin price is mainly driven by retail. Analyzing a retail-driven
marketplace renders the study of digital currencies like BTC unique and
different from the well studied equity options markets, where retail
only has a minor influence (Bloomberg 2021).

Another interesting feature of the market under consideration is not
just the dominating presence of retailers, but their easy access to
leverage for speculation. Since Deribit is by design a margin-trading
platform, levers of up to 100 are available for longs. Easy access to
leverage could suggest the existence of the leverage effect if investors
were risk affine. However, we cannot confrm a leverage effect to be
present in the time frame under consideration.

@@

\section{Pricing Kernels}

Assume a risky asset with a stochastic price process
\(\{S_t\}_{t \in \mathbb{N}}\) and a risk-free interest rate
\(\{r_t\}_{t \in \mathbb{N}}\) in a complete market. Following the
second Fundamental Theorem of Asset Pricing, a unique
martingale-equivalent measure \(Q\) exists in the described setting,
under which derivatives can be priced in an arbitrage-free manner (Huynh
et al. 2002; Pascucci and Agliardi 2011).

Let \(C_t\) be the price at time \(t\) of a contingent claim with payoff
\(\psi(\cdot)\) on the risky asset (underlying), which has a maturity at
\(T\) and a time-to-maturity \(\tau = T-t\). For simplicity assume a
constant interest rate \(r_t = r\). The price of any such contingent
claim can be expressed as the discounted value of expected future
payoffs, weighted with their respective probabilities of occurrence. The
expectation operator is conditional on the information set at \(t\)
under the equivalent martingale probability \(Q\)

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12,
]{article}
\usepackage{lmodern}
\usepackage[table,xcdraw]{xcolor}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Empirical Option Returns and the risk-free Rate in Crypto Asset Markets},
  pdfauthor={Julian Winkel; Wolfgang K. Härdle},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.5cm]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{caption}
\usepackage{eucal}
\floatplacement{figure}{H}

\title{Pricing Kernels and Risk Premia implied in Bitcoin Options}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{7 January 2024}

@@

\singlespacing 
abstract

@@

Another, so far rarely used pathway is the assessment of the risk-return characteristics of Bitcoin through the lens of the options written on it, which allow new model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.

This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option positions in the early 2000s.

Bakshi and Shumway both found that expected call returns exceed those of the underlying and that expected put returns underperform the underlying. Both also found that the effect increases (decreases) with the strike. 
Bakshi found that zero-beta, at-the-money straddle positions produce average losses of approximately three percent per week and suggests that the reason may be a systematic volatility premium being priced in options.

Following Shumway, the risk-return characteristics of options can be separated in two elements, a leverage effect and a curvature effect due to the sensitivity of option payoffs to higher moments of the underlying. 
First, the holder (buyer) of an option is subject to a leverage effect since exposure to the underlying can be obtained through the payment of a premium, which is small compared to the price of the underlying. 
If there is a leverage effect, then (long) call options should outperform their underlying and (long) put options should underperform their underlying. Furthermore, the effect should increase (decrease) with the strike price for calls (puts).
This reasoning allows a simple test of existence and size of the leverage effect and thus conclusions about the level of speculation associated to Bitcoin valuation.

(The second component, related to the sensitivity of options towards higher moments, implies that options are redundant assets...)

If options were redundant assets, then apart of the leverage effect, delta-neutral option portfolios should earn the risk-free rate (no premium) on average.
Until now, there is no risk-free rate available in the space of crypto assets. We establish a proxy or reference rate for a possible risk-free rate, which results from the perpetual futures written on Bitcoin and Ether.

Use Deribit and Binance perpetual futures for this, equally weighted.

(This proxy is clearly not risk-free due to counterparty risk, but we argue that a carry trade involving a short position on perpetual futures on multiple platforms in conjunction with a secured, on-chain underlying position reduces the platform-induced counterparty risk (which is the residual risk in the carry trade) as far as possible.) (This also leaves liquidity risk though!!)

@@

\section{A Proxy for the risk-free Rate of Bitcoin and Ether}

Evidently, there is no established risk-free rate in crypto (or digital asset) markets. In the absence of riskless bond, we refer to the next best thing as a proxy for the risk free rate, which is the replication of the market-implied yield through a position which only has liquidity risk and counterparty risk. To be fair, counterparty risk also exists for risk-free bonds.

A large share of the trading volume in digital asset markets falls on the futures market. Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments (show both!). While it would be possible to use a yield from a long-short futures position (e.g. short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration. These are the perpetual futures, which are listed on some exchanges.

As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.

BTC Futures

Total Open Interest $1,405,918,350
Total 24h Trade Volume $324,820,482

ETH Futures
Total Open Interest $466,932,584
Total 24h Trade Volume $98,238,298

\begin{table}[]
\begin{tabular}{lll}
\textbf{Instrument}            & \textbf{Aggregate Open Interest (USD)} & \textbf{24 Hour Aggregate Trade Volume (USD)} \\
BTC Perpetual Futures & 19,343,021,437                & 50,339,886,015                       \\
ETH Perpetual Futures & 14,945,055,482                & 18,097,004,167                       \\
BTC Futures           & 1,405,918,350                 & 324,820,482                          \\
ETH Futures           & 466,932,584                   & 98,238,298                          
\end{tabular}
\end{table}

Source for liquidity: 
https://www.coingecko.com/en/derivatives
https://www.coingecko.com/en/derivatives/futures

% Source: https://www.tablesgenerator.com/#
% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage[table,xcdraw]{xcolor}
% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

As of 2024-01-07

Bitcoin Perpetuals with 
Total Open Interest \$19,343,021,437
Total 24h Trade Volume \$50,339,886,015

\begin{table}[]
\begin{tabular}{llrrrrrrr}
\textbf{Exchange}    & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\# Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
\# Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
\# BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
\# Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
\# Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
\# Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
\# Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
\# Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
\# OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
\# Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31                        
\end{tabular}
\end{table}

Ether Perpetuals

Total Open Interest \$14,945,055,482
Total 24h Trade Volume \$18,097,004,167

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage[table,xcdraw]{xcolor}
% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage[table,xcdraw]{xcolor}
% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}

\begin{table}[]
\begin{tabular}{llrrrrrrr}
\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30                     
\end{tabular}
\end{table}

BTC Futures

with

Total Open Interest $1,405,918,350
Total 24h Trade Volume $324,820,482

\begin{table}[]
\begin{tabular}{llrrrrrrr}
\textbf{Exchange}                & \textbf{Symbol}    & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Expires in}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
\# Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
\# Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
\# Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
\# Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
\# BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
\# BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
\# BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
\# BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
\# BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
\# BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
\# BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
\# BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
\# Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
\# Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
\# Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
\# Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
\# Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
\# Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
\# Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\
\# Bybit (Futures)               & BTC-26JAN24        & \$44,370.24                        & 44042.75 USDC                            & -0.773\%                           & 0.02\%                              & 19 days                                 & -                                          & \$47,245.15                             \\
\# Bybit (Futures)               & BTC-23FEB24        & \$44,806.59                        & 44042.99 USDC                            & -1.739\%                           & 0.03\%                              & about 2 months                          & -                                          & \$8,650.36                              \\
\# Crypto.com Exchange (Futures) & BTCUSD-240628      & \$46,384.20                        & 44003.38 USD                             & -5.133\%                           & 0.41\%                              & -                                       & \$24,557,224                               & \$15,659.31                             \\
\# Crypto.com Exchange (Futures) & BTCUSD-240329      & \$45,024.60                        & 44003.38 USD                             & -2.268\%                           & 0.46\%                              & -                                       & \$1,118,289                                & \$17,244.42                             \\
\# Crypto.com Exchange (Futures) & BTCUSD-240126      & \$44,215.10                        & 44003.38 USD                             & -0.479\%                           & 0.29\%                              & -                                       & \$9,701                                    & \$18,428.85                             \\
\# Crypto.com Exchange (Futures) & BTCUSD-240223      & \$44,624.00                        & 44003.38 USD                             & -1.391\%                           & 0.43\%                              & -                                       & \$3,539                                    & \$14,931.19                             \\
\# Deribit                       & BTC-29MAR24        & \$45,300.00                        & 44026.9 USD                              & -2.810\%                           & 0.02\%                              & 3 months                                & \$208,084,190                              & \$15,282,281.56                         \\
\# Deribit                       & BTC-26JAN24        & \$44,475.00                        & 44026.9 USD                              & -1.008\%                           & 0.1\%                               & 19 days                                 & \$89,621,140                               & \$3,132,087.87                          \\
\# Deribit                       & BTC-28JUN24        & \$46,577.50                        & 44026.9 USD                              & -5.476\%                           & 0.02\%                              & 6 months                                & \$79,314,230                               & \$7,916,251.72                          \\
\# Deribit                       & BTC-27SEP24        & \$47,715.00                        & 44026.9 USD                              & -7.729\%                           & 0.09\%                              & 9 months                                & \$32,099,570                               & \$1,034,939.35                          \\
\# Deribit                       & BTC-12JAN24        & \$44,110.00                        & 44026.9 USD                              & -0.188\%                           & 0.03\%                              & 5 days                                  & \$25,884,930                               & \$7,230,738.10                          \\
\# Deribit                       & BTC-23FEB24        & \$44,767.50                        & 44026.9 USD                              & -1.654\%                           & 0.03\%                              & about 2 months                          & \$22,571,940                               & \$744,850.73                            \\
\# Deribit                       & BTC-27DEC24        & \$49,247.50                        & 44026.9 USD                              & -10.601\%                          & 0.13\%                              & 12 months                               & \$11,398,600                               & \$600,503.46                            \\
\# Deribit                       & BTC-19JAN24        & \$44,222.50                        & 44026.9 USD                              & -0.442\%                           & 0.04\%                              & 12 days                                 & \$5,538,440                                & \$2,799,269.71                          \\
\# HTX Futures                   & BTC\_CQ            & \$45,297.68                        & 44023.11 USD                             & -2.814\%                           & 0.38\%                              & 3 months                                & \$1,002,200                                & \$1,602,716.03                          \\
\# HTX Futures                   & BTC\_CW            & \$44,095.65                        & 44030.71 USD                             & -0.147\%                           & 0.45\%                              & 4 days                                  & \$47,100                                   & \$1,011,419.90                          \\
\# HTX Futures                   & BTC\_NW            & \$44,211.45                        & 44023.11 USD                             & -0.426\%                           & 0.4\%                               & 11 days                                 & \$9,000                                    & \$967,082.71                            \\
\# Kraken (Futures)              & FI\_XBTUSD\_240329 & \$45,520.50                        & 44013.38 USD                             & -3.311\%                           & 0.08\%                              & 3 months                                & \$6,608,999                                & \$112,442.00                            \\
\# Kraken (Futures)              & FI\_XBTUSD\_240628 & \$46,571.50                        & 44013.38 USD                             & -5.493\%                           & 0.24\%                              & 6 months                                & \$1,929,982                                & \$275,529.00                            \\
\# Kraken (Futures)              & FI\_XBTUSD\_240126 & \$44,191.50                        & 44013.38 USD                             & -0.403\%                           & 0.4\%                               & 19 days                                 & \$300,856                                  & \$3.00                                  \\
\# Kraken (Futures)              & FF\_XBTUSD\_240329 & \$45,284.00                        & 44013.38 USD                             & -2.806\%                           & 0.11\%                              & 3 months                                & \$87                                       & \$22.68                                 \\
\# Kraken (Futures)              & FF\_XBTUSD\_240126 & \$44,307.00                        & 44013.38 USD                             & -0.663\%                           & 0.08\%                              & 19 days                                 & \$32                                       & \$4.61                                  \\
\# KuCoin Futures                & XBTMH24            & \$45,444.00                        & 44072.8 USD                              & -3.017\%                           & 0.19\%                              & 3 months                                & \$11,251,580                               & \$86,193.00                             \\
\# OKX (Futures)                 & BTC-USD-240329     & \$45,322.90                        & 44016.1 USD                              & -2.883\%                           & 0.01\%                              & 3 months                                & \$175,555,100                              & \$42,597,534.31                         \\
\# OKX (Futures)                 & BTC-USD-240628     & \$46,744.90                        & 44016.1 USD                              & -5.838\%                           & 0.03\%                              & 6 months                                & \$67,199,400                               & \$13,281,039.45                         \\
